Chicago Crime Rates Prediction

### 2022-05-31 chicago_project/report_latex/article.tex
report

\twocolumn[
    \begin{@twocolumnfalse}
        \maketitle
        \begin{abstract}
            TODO
        \end{abstract}
    \end{@twocolumnfalse}
    \vspace{1cm}
]
\onecolumn

@@

\begin{tabularx}{0.5\textwidth} { 
    | >{\raggedright\arraybackslash}X 
    | >{\centering\arraybackslash}X 
    | >{\centering\arraybackslash}X
    | >{\centering\arraybackslash}X
    | >{\centering\arraybackslash}X | }
   \hline
    &precision&recall&f1-score& support\\
   \hline
    0&  0.70& 0.87  & 0.78  & 5306 \\
    \hline
    1& 0.37 & 0.18  & 0.24  & 2292 \\
    \hline
    2& 0.37 & 0.30  & 0.33  & 451 \\
    \hline
    accuracy& & & 0.64  &  8049 \\
    \hline
    macro avg&  0.48   & 0.45 & 0.45 & 8049 \\
    \hline
    weighted avg&0.59   & 0.60 & 0.60  &  8049 \\
    \hline
  \end{tabularx}

That The precision is not so high for the Medium and High Alarm which are more important
for prediction.

\onecolumn
\appendix

@@

\subsection{Figure 4 - ARIMA results}\label{appendix:fig5}
\begin{figure}[h]
\includegraphics[width=\textwidth]{fig6.png}
\caption{Spring and Summer Crime count}
\end{figure}

\subsection{Figure 5 - Spring and Summer Crime count}\label{appendix:fig3}
\begin{figure}[h]
\includegraphics[width=\textwidth]{fig3.png}
\caption{Spring and Summer Crime count}
\end{figure}

@@

\newpage
\printbibliography

>>>>

\twocolumn[
    \begin{@twocolumnfalse}
        \maketitle
        \begin{abstract}
            By using a data-driven approach this research focuses on exploring the crime rates
            in Chicago from year 2012 to 2016 in order to find a matching pattern for crime prediction in the future.
            The primary goal of this reasearch is to predict the amount of crime, based on the date and place.
            Using strong machine learning models it was possible to predict the crime rate. However, due to the low
            accuracy of the predictions it was concluded that it is not possible to rely solely on the models produced by this research
        \end{abstract}
    \end{@twocolumnfalse}
    \vspace{1cm}
]
\onecolumn

@@

\begin{tabularx}{0.48\textwidth} { 
    | >{\raggedright\arraybackslash}X 
    | >{\centering\arraybackslash}X 
    | >{\centering\arraybackslash}X
    | >{\centering\arraybackslash}X
    | >{\centering\arraybackslash}X | }
   \hline
    &precision&recall&f1-score&support\\
   \hline
    0&0.70&0.87&0.78&5306\\
    \hline
    1&0.37&0.18&0.24&2292\\
    \hline
    2&0.37&0.30&0.33&451\\
    \hline
    accuracy&&&0.64&8049\\
    \hline
    macro avg&0.48&0.45&0.45&8049\\
    \hline
    weighted avg&0.59&0.60&0.60&8049\\
    \hline
  \end{tabularx}

that the precision is not so high for the Medium and High Alarm which are more important
in therms of accuracy.

By tuning the Classifier using Grid Search in turned out that the parameters:
\begin{itemize}
    \item Maximun depth = 10;
    \item Minimun samples per leaf = 100;
    \item Random state = 42;
\end{itemize}

are the best for this type of classification. The accuracy went up to 0.71\%.

The classification report shows:

\begin{tabularx}{0.5\textwidth} { 
    | >{\raggedright\arraybackslash}X 
    | >{\centering\arraybackslash}X 
    | >{\centering\arraybackslash}X
    | >{\centering\arraybackslash}X
    | >{\centering\arraybackslash}X | }
   \hline
    &precision&recall&f1-score&support\\
   \hline
    0&0.79&0.87&0.83&5306\\
    \hline
    1&0.53&0.42&0.47&2292\\
    \hline
    2&0.37&0.30&0.33&451\\
    \hline
    accuracy&&&0.71&8049\\
    \hline
    macro avg&0.56&0.53&0.54&8049\\
    \hline
    weighted avg&0.69&0.71&0.70&8049\\
    \hline
  \end{tabularx}

that even though the accuracy went slightly up, the most important predictions(Medium and High Crime rate) are still
low on the scale.

\section{Conclusion}
Based on this research, it can be concluded that time and place are factors which influence the number and type of crimes in a specific district, 
which could help police to distribute their resources better by planning where and how many officers should be deployed to patrol. 
Is this information enough for an artificial intelligence model to predict where and which type of crime could happen? 
Clearly not, as the behavior of human beings is not so easy to predict, usually it is influenced by a lot of external factors which are very important. 
Covid-19 was a factor that changed people's behavior and their mental health \cite{kim2021exploring}. Therefore, crime amount and their types changed significantly during lockdowns. 
Restrictions also caused limitations in people's movement. It is not ethical to use such models to predict crime, it is a very sensitive subject as current generation tends to prioritize each human life and the job of the state is to protect it.

\onecolumn
\printbibliography
\newpage

\appendix

@@

\subsection{Figure 4 - ARIMA results}\label{appendix:fig5}
\begin{figure}[h]
\includegraphics[width=\textwidth]{fig6.png}
\caption{Spring and Summer Crime count}
\end{figure}
\newpage

\subsection{Figure 5 - Spring and Summer Crime count}\label{appendix:fig3}
\begin{figure}[h]
\includegraphics[width=\textwidth]{fig3.png}
\caption{Spring and Summer Crime count}
\end{figure}
\newpage

@@
